Applied Measure Theory for Probabilistic Modeling

### 2022-05-17 paper/paper.tex
edits

We'll now describe some foundations to help the reader get a deeper understanding of our approach, in particular what measures and probability distributions are and how they relate to notions such as the probability of something happening in the real world or the notion of volume of the space we are living in. 
\chad{Above sentence is very long, can we break it up?}

@@

 Then we also know that the answer to the complement $A^c$ (no or yes), and we always know that $\Omega$ has probability 1 and the corresponding question is answered by `yes'. Likewise, if both $A$ and $B$ can be answered given what we know, we also know the answer to $A \cup B$. That means, these known events form an $\sigma$-algebra, and in particular for each random variable $\bX$ there is a $\sigma$-algebra associated with $\bX$ which encodes what else we know knowing $\bX$ and how we should assign (conditional) probabilities to other events knowing $\bX$.

 This is a very relevant question for probabilistic programming tasks and causal inference, and with \emph{kernels} (Section~\ref{Kernels}) \verb|MeasureTheory| does provide tools to reason about it which are computationally appropriate, because they are local.

\chad{above paragraph needs editing}

>>>>

We'll now describe some foundations to help the reader get a deeper understanding of our approach. In particular, we'll define \emph{measures} and \emph{probability distributions}, relate them to familiar notions such as \emph{volume} and the \emph{probability of an event}.

@@

 Then we also know that the answer to the complement $A^c$ (no or yes), and we always know that $\Omega$ has probability 1 and the corresponding question is answered by `yes'. Likewise, if both $A$ and $B$ can be answered given what we know, we also know the answer to $A \cup B$.

 As the reader might now suspect, such known events form a $\sigma$-algebra. In particular, for each random variable $\bX$ there is a $\sigma$-algebra associated with $\bX$ that encodes what else we know knowing $\bX$ and how we should assign (conditional) probabilities to other events knowing $\bX$.

 This is a very relevant question for probabilistic programming tasks and causal inference. But we've already mentioned that \verb|MeasureTheory| does not explicitly represent $\sigma$-algebras. Instead, questions like these can be addressed using \emph{kernels} (Section~\ref{Kernels}). These give a way to reason about local behavior, and be much more computationally efficient.
